Notes for General Relativity

### 2016-09-10 G.R/G.R.tex
Daily update.

>>>>

    \subsection{Lorentz Transformation}
    \label{sec:Lorentz_Transformation}

    Next we have to consider the coordinate transformations in
    four-dimensional spacetime. The formula can be obtained solely by
    the restricting transformation to be an isometry.

    These transformations are categorize into two groups: parallel
    displacement and rotation. Only formula for rotation is worth
    consideration. Rotation in spacetime, simiilar to their
    counterparts in $\mathbb{R}^3$, can be decomposed according to
    six axes of rotation, each representing rotation in plane
    $xy,xz,yz,xt,yt,zt$. The first of this is only ordinary spatial
    rotation. The rest are called \textit{Lorentz Transformations}.
    And there is really only one important formula, one for 
    rotation around $xt$ plane:
    \begin{align}
        x = x'\cosh\psi + t \sinh\psi\text{, }
        t = x'\sinh\psi + t \cosh\psi
    \end{align}
    where $\psi$ is the "angle of rotation". However, this "angle"
    do not have much physical interpretation. Instead, the following
    formula is more useful, which relates the coordinate in frame
    $K$, to anther fram $K'$ moving in uniform velocity $v$ w.r.t
    $K$:
    \begin{align}
        x = \frac{x'+vt'}{\sqrt{1-v^2}}\nonumber\\
        y = y'\text{, }z = z' \nonumber\\
        t = \frac{t'+v x'}{\sqrt{1-v^2}}
    \end{align}

    Aided with this formula, Landau discusses the \textit{Lorentz
    contraction} phenomenon in special relativity and defines
    the proper length\nomenclature{proper length}{\nomrefpage}
    $l_0$, defined as the length in its rest frame. It is related
    to its length measured in another frame $K'$ by:
    \begin{align}
        l' = l_0 \sqrt{1-v^2}
    \end{align}

    Finally he mentions that, since Lorentz transformations are
    in fact rotations, they naturally do not commute, unless the
    rotation is fixed in only one plane.
